cardinalR: Generating Interesting High-Dimensional Data Structures

### 2025-12-08 paper-cardinalR.Rmd
Added table caption

Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:branching-tb-html)', '\\@ref(tab:branching-tb-pdf)'))` outlines these functions. The main arguments of the functions described in Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:arg-branching-tb-html)', '\\@ref(tab:arg-branching-tb-pdf)'))`.

@@

branch_tb <- tibble(fun = c("gen_expbranches",

@@

```{r branching-tb-html, eval=knitr::is_html_output()}
branch_tb |> 
  mutate(parm = paste0("<code>", parm, "</code>")) |>
  mutate(fun = paste0("<code>", fun, "</code>")) |> 
  kable(caption = "cardinalR branching data generation functions", col.names = c("Function", "Arguments", "Explanation"), escape = FALSE, table.pos = "!ht") 
```

```{r branching-tb-pdf, eval=knitr::is_latex_output()}
branch_tb |>
  mutate(parm = paste0("\\texttt{", parm, "}")) |>
  mutate(fun = paste0("\\texttt{", fun, "}")) |> 
  kable(caption = "cardinalR branching data generation functions", format="latex", col.names = c("Function", "Arguments", "Explanation"), escape = FALSE, booktabs = T, table.pos = "!ht", linesep = "")  |>
  column_spec(1, width = "3.5cm") |>
  column_spec(2, width = "1.5cm") |>
  column_spec(3, width = "8cm")
```

@@

```{r arg-branching-tb-html, eval=knitr::is_html_output()}
arg_branching_tb |> 
  mutate(arg = paste0("<code>", arg, "</code>")) |>
  kable(caption = "The main arguments for branching shape generators.", col.names = c("Argument", "Type", "Explanation"), escape = FALSE, table.pos = "!ht") 
```

```{r arg-branching-tb-pdf, eval=knitr::is_latex_output()}
arg_branching_tb |> 
  mutate(arg = paste0("\\texttt{", arg, "}")) |> 
  kable(caption = "The main arguments for branching shape generators.", format="latex", col.names = c("Argument", "Type", "Explanation"), booktabs = T, escape = FALSE, table.pos = "!ht")  |>
  column_spec(1, width = "1cm") |>
  column_spec(1, width = "2cm") |>
  column_spec(2, width = "3cm")
```

>>>>

Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:shape-tb-html)', '\\@ref(tab:shape-tb-pdf)'))` outlines these functions. The main arguments of the functions described in Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:arg-shape-tb-html)', '\\@ref(tab:arg-shape-tb-pdf)'))`.

@@

shape_tb <- tibble(fun = c("gen_expbranches",

@@

```{r shape-tb-html, eval=knitr::is_html_output()}
shape_tb |> 
  mutate(parm = paste0("<code>", parm, "</code>")) |>
  mutate(fun = paste0("<code>", fun, "</code>")) |> 
  kable(caption = "Overview of shape-generation functions, including their required parameters and a brief description of each geometric structure produced. The generators cover branching patterns, spheres, spirals, pyramids, Gaussian clouds, and other nonlinear shapes.", col.names = c("Function", "Arguments", "Explanation"), escape = FALSE, table.pos = "!ht") 
```

```{r shape-tb-pdf, eval=knitr::is_latex_output()}
shape_tb |>
  mutate(parm = paste0("\\texttt{", parm, "}")) |>
  mutate(fun = paste0("\\texttt{", fun, "}")) |> 
  kable(caption = "Overview of shape-generation functions, including their required parameters and a brief description of each geometric structure produced. The generators cover branching patterns, spheres, spirals, pyramids, Gaussian clouds, and other nonlinear shapes.", format="latex", col.names = c("Function", "Arguments", "Explanation"), escape = FALSE, booktabs = T, table.pos = "!ht", linesep = "")  |>
  column_spec(1, width = "3.5cm") |>
  column_spec(2, width = "1.5cm") |>
  column_spec(3, width = "8cm")
```

@@

```{r arg-shape-tb-html, eval=knitr::is_html_output()}
arg_branching_tb |> 
  mutate(arg = paste0("<code>", arg, "</code>")) |>
  kable(caption = "The main arguments for branching shape generators.", col.names = c("Argument", "Type", "Explanation"), escape = FALSE, table.pos = "!ht") 
```

```{r arg-shape-tb-pdf, eval=knitr::is_latex_output()}
arg_branching_tb |> 
  mutate(arg = paste0("\\texttt{", arg, "}")) |> 
  kable(caption = "The main arguments for branching shape generators.", format="latex", col.names = c("Argument", "Type", "Explanation"), booktabs = T, escape = FALSE, table.pos = "!ht")  |>
  column_spec(1, width = "1cm") |>
  column_spec(1, width = "2cm") |>
  column_spec(2, width = "3cm")
```

### 2025-12-08 paper-cardinalR.tex
Added table caption

Table \ref{tab:branching-tb-pdf} outlines these functions. The main arguments of the functions described in Table \ref{tab:arg-branching-tb-pdf}.

@@

\caption{\label{tab:branching-tb-pdf}cardinalR branching data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3.5cm}>{\raggedright\arraybackslash}p{1.5cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Arguments & Explanation\\
\midrule
\texttt{gen\_expbranches} & \texttt{n, k} & Exponential shaped branches.\\
\texttt{gen\_linearbranches} & \texttt{n, k} & Linear shaped branches.\\
\texttt{gen\_curvybranches} & \texttt{n, k} & Curvy shaped branches.\\
\texttt{gen\_orglinearbranches} & \texttt{n, p, k} & Linear shaped branches originated in one point.\\
\texttt{gen\_orgcurvybranches} & \texttt{n, p, k} & Curvy shaped branches originated in one point.\\
\texttt{gen\_cone} & \texttt{n, p, h, ratio} & Cone-shaped structure.\\
\texttt{gen\_gridcube} & \texttt{n, p} & Cube with specified grid points along each axes.\\
\texttt{gen\_unifcube} & \texttt{n, p} & Cube with uniform points.\\
\texttt{gen\_gaussian} & \texttt{n, p, s} & Multivariate Gaussian cloud.\\
\texttt{gen\_longlinear} & \texttt{n, p} & Long linear structure.\\
\texttt{gen\_mobius} & \texttt{n} & Möbius strip in $3  ext{-}D$.\\
\texttt{gen\_quadratic} & \texttt{n} & Quadratic pattern in $2  ext{-}D$.\\
\texttt{gen\_cubic} & \texttt{n} & Cubic pattern in $2  ext{-}D$.\\
\texttt{gen\_pyrrect} & \texttt{n, p} & Rectangular-base, with a sharp or blunted apex.\\
\texttt{gen\_pyrtri} & \texttt{n, p} & Triangular-base, with a sharp or blunted apex.\\
\texttt{gen\_pyrstar} & \texttt{n, p} & Star-shaped base, with a sharp or blunted apex.\\
\texttt{gen\_pyrfrac} & \texttt{n, p} & Pyramid with triangular pyramid-shaped holes.\\
\texttt{gen\_scurve} & \texttt{n} & S-curve in $3   ext{-}D$.\\
\texttt{gen\_circle} & \texttt{n, p} & Circle.\\
\texttt{gen\_curvycycle} & \texttt{n, p} & Curvy cell cycle.\\
\texttt{gen\_unifsphere} & \texttt{n, r} & Uniform ball.\\
\texttt{gen\_hollowsphere} & \texttt{n, p} & Hollow sphere.\\
\texttt{gen\_gridedsphere} & \texttt{n} & Grided sphere.\\
\texttt{gen\_clusteredspheres} & \texttt{n, k, r, loc} & Multiple small spheres within a big sphere.\\
\texttt{gen\_hemisphere} & \texttt{n, p} & Hemisphere.\\
\texttt{gen\_swissroll} & \texttt{n, w} & Swissroll structure.\\
\texttt{gen\_trefoil4d} & \texttt{n, steps} & Trefoil in $4\text{-}D$.\\
\texttt{gen\_trefoil3d} & \texttt{n, steps} & Trefoil in $3\text{-}D$.\\
\texttt{gen\_crescent} & \texttt{n} & Crescent pattern.\\
\texttt{gen\_curvycylinder} & \texttt{n, h} & Curvy cylinder.\\
\texttt{gen\_sphericalspiral} & \texttt{n, spins} & Spherical spiral.\\
\texttt{gen\_helicalspiral} & \texttt{n} & Helical spiral.\\
\texttt{gen\_conicspiral} & \texttt{n, spins} & Conic spiral.\\
\texttt{gen\_nonlinear} & \texttt{n, hc, non\_fac} & Nonlinear hyperbola.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:arg-branching-tb-pdf}The main arguments for branching shape generators.}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{2cm}>{\raggedright\arraybackslash}p{3cm}l}
\toprule
Argument & Type & Explanation\\
\midrule
\texttt{n} & integer & Number of points.\\
\texttt{k} & integer & Number of clusters.\\
\texttt{p} & integer & Number of dimensions.\\
\bottomrule
\end{tabular}
\end{table}

>>>>

Table \ref{tab:shape-tb-pdf} outlines these functions. The main arguments of the functions described in Table \ref{tab:arg-shape-tb-pdf}.

@@

\caption{\label{tab:shape-tb-pdf}Overview of shape-generation functions, including their required parameters and a brief description of each geometric structure produced. The generators cover branching patterns, spheres, spirals, pyramids, Gaussian clouds, and other nonlinear shapes.}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3.5cm}>{\raggedright\arraybackslash}p{1.5cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Arguments & Explanation\\
\midrule
\texttt{gen\_expbranches} & \texttt{n, k} & Exponential shaped branches.\\
\texttt{gen\_linearbranches} & \texttt{n, k} & Linear shaped branches.\\
\texttt{gen\_curvybranches} & \texttt{n, k} & Curvy shaped branches.\\
\texttt{gen\_orglinearbranches} & \texttt{n, p, k} & Linear shaped branches originated in one point.\\
\texttt{gen\_orgcurvybranches} & \texttt{n, p, k} & Curvy shaped branches originated in one point.\\
\texttt{gen\_cone} & \texttt{n, p, h, ratio} & Cone-shaped structure.\\
\texttt{gen\_gridcube} & \texttt{n, p} & Cube with specified grid points along each axes.\\
\texttt{gen\_unifcube} & \texttt{n, p} & Cube with uniform points.\\
\texttt{gen\_gaussian} & \texttt{n, p, s} & Multivariate Gaussian cloud.\\
\texttt{gen\_longlinear} & \texttt{n, p} & Long linear structure.\\
\texttt{gen\_mobius} & \texttt{n} & Möbius strip in $3  ext{-}D$.\\
\texttt{gen\_quadratic} & \texttt{n} & Quadratic pattern in $2  ext{-}D$.\\
\texttt{gen\_cubic} & \texttt{n} & Cubic pattern in $2  ext{-}D$.\\
\texttt{gen\_pyrrect} & \texttt{n, p} & Rectangular-base, with a sharp or blunted apex.\\
\texttt{gen\_pyrtri} & \texttt{n, p} & Triangular-base, with a sharp or blunted apex.\\
\texttt{gen\_pyrstar} & \texttt{n, p} & Star-shaped base, with a sharp or blunted apex.\\
\texttt{gen\_pyrfrac} & \texttt{n, p} & Pyramid with triangular pyramid-shaped holes.\\
\texttt{gen\_scurve} & \texttt{n} & S-curve in $3   ext{-}D$.\\
\texttt{gen\_circle} & \texttt{n, p} & Circle.\\
\texttt{gen\_curvycycle} & \texttt{n, p} & Curvy cell cycle.\\
\texttt{gen\_unifsphere} & \texttt{n, r} & Uniform ball.\\
\texttt{gen\_hollowsphere} & \texttt{n, p} & Hollow sphere.\\
\texttt{gen\_gridedsphere} & \texttt{n} & Grided sphere.\\
\texttt{gen\_clusteredspheres} & \texttt{n, k, r, loc} & Multiple small spheres within a big sphere.\\
\texttt{gen\_hemisphere} & \texttt{n, p} & Hemisphere.\\
\texttt{gen\_swissroll} & \texttt{n, w} & Swissroll structure.\\
\texttt{gen\_trefoil4d} & \texttt{n, steps} & Trefoil in $4\text{-}D$.\\
\texttt{gen\_trefoil3d} & \texttt{n, steps} & Trefoil in $3\text{-}D$.\\
\texttt{gen\_crescent} & \texttt{n} & Crescent pattern.\\
\texttt{gen\_curvycylinder} & \texttt{n, h} & Curvy cylinder.\\
\texttt{gen\_sphericalspiral} & \texttt{n, spins} & Spherical spiral.\\
\texttt{gen\_helicalspiral} & \texttt{n} & Helical spiral.\\
\texttt{gen\_conicspiral} & \texttt{n, spins} & Conic spiral.\\
\texttt{gen\_nonlinear} & \texttt{n, hc, non\_fac} & Nonlinear hyperbola.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:arg-shape-tb-pdf}The main arguments for branching shape generators.}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{2cm}>{\raggedright\arraybackslash}p{3cm}l}
\toprule
Argument & Type & Explanation\\
\midrule
\texttt{n} & integer & Number of points.\\
\texttt{k} & integer & Number of clusters.\\
\texttt{p} & integer & Number of dimensions.\\
\bottomrule
\end{tabular}
\end{table}
